They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: git issues
Made Zombunnies smaller, added spawn points, and increased spawn rate and population size.

Players, on the other hand, may also learn to optimize around our implementation
of evolution. Conceivably clever player could develop two very different
strategies ahead of time. The player would first implement the weaker strategy,
and as soon as the Zombunnies have deeply rooted themselves in the local maximum
versus that strategy, the strategy could be changed to the second strategy,
leaving the Zombunnies unable to easily adapt to the new strategy.

@@

Conceptually, evolving neural nets instead of using backpropagation
has the massive benefit of not worrying about how to differentiate and nicely
back-propagate the reward/fitness function to learn, which opens up the
possibility to drop in a nerual net to replace any function in a learning
environment; on a larger timescale, the selection tournament process itself
could modeled with a recurrent neural network, and evolved over multiple plays
of the game.

>>>>

Players, on the other hand, may also learn to optimize around our implementation
of evolution. Conceivably clever players could develop two very different
strategies ahead of time. The player would first implement the weaker strategy,
and as soon as the Zombunnies have deeply rooted themselves in the local maximum
versus that strategy, the strategy could be changed to the second strategy,
leaving the Zombunnies unable to easily adapt to the new strategy.

@@

Conceptually, evolving neural nets instead of using backpropagation
has the massive benefit of not worrying about how to differentiate and nicely
back-propagate the reward/fitness function to learn, which opens up the
possibility to drop in a neural net to replace any function in a learning
environment; on a larger timescale, the selection tournament process itself
could modeled with a recurrent neural network, and evolved over multiple plays
of the game.
